### 2021-02-22 architecture.tex
architecture notes

The architecture is designed so that the recommender can be trained
on the results of \gls{atp} executions on various problems with random precedences.
Since the recommender contains a neural network,
it is parameterized by weight tensors
whose values can be trained by gradient descent.
\todo{Ensure we have defined ``gradient descent''.}
\todo{MS: chapu ucel (a vidim, ze dalsi veta navazuje na ``parameters'', ale je to kostrbate.
Recommender = system, chapu jako program. Programy vetsinou neparametrizujeme tenzorama a gradient descent zije na jine urovni,
nez aby parametrizovane programy primo ucil. Uceni je spis nejaka technologie, kterou recommender pouziva, aby ... ``produces precedences
that are likely to yield a successful proof''.  }
The goal of the training is to find parameter values
such that the recommender produces precedences
that are likely to yield a successful proof in few iterations of the saturation loop.

The recommender consists of modules that perform specific subtasks,
each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
\begin{enumerate}
\item Graphifier converts the input \gls{cnf} problem into a problem graph.
\item \Gls{gcn} converts a problem graph into symbol embeddings.
\item Output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
\item Ranking converts the symbol costs into a symbol precedence.
It is only used in generating mode.
\item Loss function converts the symbol costs and a pair of precedences into a loss value.
It is only used in training mode.
\end{enumerate}
\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
embedding, \gls{gcn}/convolution layers, ... \\
FB: Staci predestrit, ze detaily vysvetlim pozdeji?}

@@

As the first step of the recommender processing pipeline,
the input problem is converted from a \gls{cnf} representation
to a \emph{heterogeneous (directed) graph} \cite{Zhou2018}.
% Zhou uses the term "heterogeneous graph".
%\footnote{Data mining literature often uses the term \gls{hin} \cite{Shi2015} for heterogeneous graphs.
%We prefer to conform to the terminology common in literature studying \glspl{gnn}.}
Each of the nodes is labeled with a node type,
and each edge is labeled with an edge type,
defining the heterogeneous nature of the graph.
Each node corresponds to one of the elements that constitute the \gls{cnf} formula,
such as a clause, an atom or a predicate symbol.
Each such category of elements corresponds to one node type.
The edges represent the (oriented) relations between the elements,
for example the incidence relation between a clause and one of its (literals') atoms,
or the relation between an atom and its predicate symbol.
\Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
\Cref{fig:GcnExample} shows an example of a graph representation of a simple problem.

@@

The graph representation has the following properties:
\begin{itemize}
\item Lossless: The original problem can be faithfully reconstructed from the corresponding graph representation
(up to logical equivalence).
\item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
\item For each relation $r$, its inverse $\inv{r}$ is also present in the graph,
typically represented by a different edge type.
\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?\\
FB: Chci vyjasnit, ze inverzni edge ma jiny edge type.}
\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
\item The polarity of the literals is expressed by the type of the edge (\epos{} or \eneg{})
connecting the respective atom to the clause it occurs in.
\item For every non-equality atom and term, the order of its arguments is captured by a sequence of \ntype{argument} nodes chained by edges \cite{Rawson2020}.
\item The two operands of equality are not ordered.
This reflects the symmetry of equality.
\item Perfect sub-expression sharing:
\todo{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.}
Redundant atoms and terms share a node representation \cite{}.
Note that since each variable is bound by a clause,
ground terms are shared across clauses,
but non-ground terms are only shared within the context of a clause.
\todo{FB: Remove as of little interest?}
\end{itemize}
\todo{FB: Reference appendix if we describe the representation in more detail there.}
\todo[inline]{MS: Filosoficka k ``can be represented''; mozna by se mohlo nekde objevit:
Snazime se do struktury HIN ``otisknout'' celou strukturu CNF (jak jsem rikal,
znamena to, ze zobrazeni je proste), abychom siti nevzali moznost ``vedet o problemu
uplne vsechno'' (az na veci, na kterych nezalezi jako poradi literaly v klauzulich, etc).
Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi), ale my nevime, jak takovy zvolit.\\
FB: Zkusim to popsat, kdyz zbyde cas.}
\todo{FB: Mention other encodings that have been proposed by Mirek and Michael.}

@@

For each symbol in the problem,
we seek to find a vector representation, i.e., an \emph{embedding},
that captures the symbol's properties that are relevant
for correctly ranking the symbol in the observed symbol precedences.
\todo{FB: What does "correct" mean?}
The symbol embeddings are output by a \gls{rgcn} \cite{Schlichtkrull2017},
which is a stack of graph convolutional layers.
Each layer consists of a collection of differentiable modules---one module per edge type.
The computation of the \gls{gcn} starts with assigning each node an initial embedding
and then repeatedly updates the embeddings by passing them through convolutional layers.
\todo{FB: Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.}

@@

One pass through the convolutional layer
updates the node embeddings by passing a message along each of the edges.
For an edge of type $r \in \mathcal{R}$ going from source node $s$ to destination node $d$ at layer $l$,
the message is composed by converting the embedding of the source node $h_s^{(l)}$
using the module associated with the edge type $r$.
In the simple case that the module is a dense layer with weights $W_r^{(l)}$,
\todo{MS: hnidopich nevi, co to znamena ``dense layer''}
the message is $h_s^{(l)} W_r^{(l)}$.
Each message is then divided by a normalization constant
$c_{s,d} = \sqrt{\card{\mathcal{N}_s^r}} \sqrt{\card{\mathcal{N}_d^r}}$ \cite{kipf2017semisupervised},
where $\mathcal{N}_n^r$ is the set of neighbors of node $n$ under the relation $r$.
\todo{FB: Mention that we mean both in- and out-neighbors?}
Once all the messages are computed,
they are aggregated by the destination nodes to form the new node embedding.
Each node $d$ aggregates all the incoming messages of a given edge type $r$ by summation,
then passes the sum through an activation function $\sigma$ such as the \gls{relu},
and finally aggregates the messages across the edge types by summation,
yielding the new embedding $h_d^{(l+1)}$.
The following formula captures the update of embedding of node $d$:
$$
h_d^{(l+1)} =
\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (h_s^{(l)} W_r^{(l)} + b_r^{(l)})}
$$
%$$
%h_i^{(l+1)} =
%\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
%$$
% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
%\todo{FB: Mention inspiration: Transformer. See Straka's slides.}

@@

The symbol cost of each symbol is computed by passing the symbol's embedding through a dense layer with a single output unit.
No activation function is applied so that the output values can span the whole $\re$.

Note that it is possible to use a more complex projection module,
e.g., a feed-forward network with one or more hidden layers.
\todo{FB: Ensure the term is defined.}
Our experiments showed no significant improvement when a hidden layer is added,
arguably because the underlying \gls{gcn} learns a sufficiently complex transformation.

@@

\begin{proof}
We prove the lemma by contradiction.
Let $\pi$ minimize $C$ and let $\pi$ not rank the costs in non-increasing order.
Then there exist $k < l$ such that $c(\pi(k)) < c(\pi(l))$.
Let $\bar{\pi}$ be a precedence obtained from $\pi$ by swapping the elements $k$ and $l$.
%$\bar{\pi} = (\pi(1), \ldots, \pi(k-1), \pi(l), \pi(k+1), \ldots, \pi(l-1), \pi(k), \pi(l+1), \ldots, \pi(n))$.
\begin{align*}
C(\bar{\pi}) - C(\pi)
&= kc(\bar{\pi}(k)) + lc(\bar{\pi}(l)) - kc(\pi(k)) - lc(\pi(l)) \\
&= kc(\pi(l)) + lc(\pi(k)) - kc(\pi(k)) - lc(\pi(l)) \\
&= k(c(\pi(l)) - c(\pi(k))) - l(c(\pi(l)) - c(\pi(k))) \\
&= (k-l) (c(\pi(l)) - c(\pi(k))) \\
&< 0
\end{align*}
The final inequality is due to the assumption that $k-l < 0$ and
$c(\pi(l)) - c(\pi(k)) > 0$.
Thus, $C(\bar{\pi}) < C(\pi)$, which is contradicts the assumption that $\pi$ minimizes $C$. \qed
\end{proof}

Once the symbol costs are known,
producing a precedence that minimizes the precedence cost is cheap
because ranking is a fast operation.

Note that the precedence that minimizes $C$
orders the symbols with the lowest cost as the last,
prioritizing them for early inferences.

\todo[inline]{FB: Why is the equality predicate always the first in the precedence?}
\todo[inline]{FB: Mention that the common heuristics fit this scheme.}

@@

In \cref{sec:graphifier,sec:gcn,sec:output,sec:ranking} we described the structure of a recommender system that generates a precedence for an arbitrary input problem.
The efficacy of the recommender depends on the quality of the underlying symbol cost function.
In theory, the symbol cost function can assign the costs so that
ranking the symbols by their costs yields an optimum precedence,
and all the information necessary to determine the optimum precedence is present in the graph representation of the input problem.
Our approach to defining an appropriate symbol cost function is based on statistical learning
from executions of an \gls{atp} on a set of problems with various precedences.

@@

Each training example has the form $(P, \PrecBetter, \PrecWorse)$,
where $P = (\Sigma, \mathit{Cl})$ is a problem
and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
such that $\PrecBetter$ solves $P$ in fewer iterations of the saturation loop than $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}$.
\todo{Is this sufficient?}

@@

\todo{Two levels of proxy metrics: 0-1 loss, differentiable loss (hinge, logistic)}

To ensure that ranking the symbols by their costs
yields a good precedence,
we want the symbol cost function $c$
to satisfy the inequality $C(\PrecBetter) < C(\PrecWorse)$
which can alternatively be expressed as $s(\PrecBetter, \PrecWorse) = C(\PrecBetter) - C(\PrecWorse) < 0$.
We consider the value $s(\PrecBetter, \PrecWorse)$
to be the score of the (ordered) precedence pair $(\PrecBetter, \PrecWorse)$.
Given a set of examples of the form $(P, \PrecBetter, \PrecWorse)$
where $\Better{\PrecBetter}{\PrecWorse}$,
our goal is to maximize the accuracy
$\frac{1}{m} \sum_x \iverson{s(\PrecBetter, \PrecWorse) < 0}$.
% Alternative: We actually don't care about the relative order of non-minimum precedences.

A common approach to training a binary classifier is to relax the non-differentiable accuracy $[s(\PrecBetter, \PrecWorse) < 0]$
to a differentiable proxy
such as the logistic loss
$L = - \log \sigmoid s(\PrecBetter, \PrecWorse)$.

>>>>

The architecture is designed so that the recommender can be trained
on the results of \gls{atp} executions on various problems with random precedences.
Since the recommender contains a neural network,
it is parameterized by weight tensors
whose values can be trained by gradient descent.
\todo{Ensure we have defined ``gradient descent''.}
\todo{MS: chapu ucel (a vidim, ze dalsi veta navazuje na ``parameters'', ale je to kostrbate.
Recommender = system, chapu jako program. Programy vetsinou neparametrizujeme tenzorama a gradient descent zije na jine urovni,
nez aby parametrizovane programy primo ucil. Uceni je spis nejaka technologie, kterou recommender pouziva, aby ... ``produces precedences
that are likely to yield a successful proof''.  }
The goal of the training is to find parameter values such that the recommender produces precedences
that are likely to yield a successful proof in as few iterations of the saturation loop as possible.\todo{MS: mozna udernejsi?}

The recommender consists of modules that perform specific subtasks,
each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
\begin{enumerate}
\item Graphifier converts the input \gls{cnf} problem into a problem graph.
\item \Gls{gcn} converts a problem graph into symbol embeddings.
\todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
Ale v te prislusne podsekci tim zas zacit.}
\item An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?}
\item Ranking converts the symbol costs into a symbol precedence.
It is only used in generating mode.
\item Loss function converts the symbol costs and a pair of precedences into a loss value.
It is only used in training mode.
\end{enumerate}
\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
embedding, \gls{gcn}/convolution layers, ... \\
FB: Staci predestrit, ze detaily vysvetlim pozdeji? MS: asi jo :)}

@@

As the first step of the recommender processing pipeline,
the input problem is converted from a \gls{cnf} representation
to a \emph{heterogeneous (directed) graph} \cite{Zhou2018}.
% Zhou uses the term "heterogeneous graph".
%\footnote{Data mining literature often uses the term \gls{hin} \cite{Shi2015} for heterogeneous graphs.
%We prefer to conform to the terminology common in literature studying \glspl{gnn}.}
Each of the nodes is labeled with a node type,
and each edge is labeled with an edge type,
defining the heterogeneous nature of the graph.
Each node corresponds to one of the elements that constitute the \gls{cnf} formula,
such as a clause, an atom or a predicate symbol.
Each such category of elements corresponds to one node type.
The edges represent the (oriented) relations between the elements,
for example the incidence relation between a clause and one of its (literals') atoms,
or the relation between an atom and its predicate symbol.
\Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
\Cref{fig:GcnExample}\todo{MS: ten se mi libi!} shows an example of a graph representation of a simple problem.

@@

The graph representation has the following properties:
\begin{itemize}
\item Lossless: The original problem can be faithfully reconstructed from the corresponding graph representation
(up to logical equivalence).
\item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
\item For each relation $r$, its inverse $\inv{r}$ is also present in the graph,
typically represented by a different edge type.
\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?\\
FB: Chci vyjasnit, ze inverzni edge ma jiny edge type.}
\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
\item The polarity of the literals is expressed by the type of the edge (\epos{} or \eneg{})
connecting the respective atom to the clause it occurs in.
\item For every non-equality atom and term, the order of its arguments is captured by a sequence of \ntype{argument} nodes chained by edges \cite{Rawson2020}.
\item The two operands of equality are not ordered.
This reflects the symmetry of equality.
\item Perfect sub-expression sharing:
\todo{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.
MS: O to my, neslo. Slo o to, jestli se sdily ground termy mezi klauzulemi, ted uz dobry! :)}
Redundant atoms and terms share a node representation \cite{}.
\todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''.}
Note that since each variable is bound by a clause,
ground terms are shared across clauses,
but non-ground terms are only shared within the context of a clause.
\todo{FB: Remove as of little interest?}
\end{itemize}
\todo{FB: Reference appendix if we describe the representation in more detail there.}
\todo[inline]{MS: Filosoficka k ``can be represented''; mozna by se mohlo nekde objevit:
Snazime se do struktury HIN ``otisknout'' celou strukturu CNF (jak jsem rikal,
znamena to, ze zobrazeni je proste), abychom siti nevzali moznost ``vedet o problemu
uplne vsechno'' (az na veci, na kterych nezalezi jako poradi literaly v klauzulich, etc).
Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi), ale my nevime, jak takovy zvolit.\\
FB: Zkusim to popsat, kdyz zbyde cas.}
\todo{FB: Mention other encodings that have been proposed by Mirek and Michael.}

@@

For each symbol in the problem,
we seek to find a vector representation, i.e., an \emph{embedding},
that captures the symbol's properties that are relevant
for correctly ranking the symbol in the observed symbol precedences.
\todo{FB: What does "correct" mean? MS: nic moc, ale v prvnim paragrafu sekce se to snad snese a zni to imho dobre:)
Nebo mas lepsi napad? "successfully"?
Napsat presne ale strucne, ze ty embeddingy jsou takove, aby siti pomohly mit co nejnizsi loss na proxy tasku 
hadani dvojic otazek, bude o dost tezsi...}
The symbol embeddings are output by a \gls{rgcn} \cite{Schlichtkrull2017},
which is a stack of graph convolutional layers.
Each layer consists of a collection of differentiable modules---one module per edge type.
The computation of the \gls{gcn} starts with assigning each node an initial embedding
and then repeatedly updates the embeddings by passing them through convolutional layers.
\todo{MS: to se mi libi, ze to nekde zacina a nekam to smeruje.}
\todo{FB: Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.
MS: (convolutional, layers, ...)}

@@

One pass through the convolutional layer
updates the node embeddings by passing a message along each of the edges.
For an edge of type $r \in \mathcal{R}$ going from source node $s$ to destination node $d$ at layer $l$,
the message is composed by converting the embedding of the source node $h_s^{(l)}$
using the module associated with the edge type $r$.
In the simple case that the module is a dense layer with weight matrix $W_r^{(l)}$,
\todo{MS: hnidopich nevi, co to znamena ``dense layer''}
the message is $h_s^{(l)} W_r^{(l)}$.\todo{MS: mas nejakou preferenci pro column/row vectors a z jake strany je prirozene nasobit?
Ja bych mozna spis psal $W_r^{(l)} h_s^{(l)}$, a mozna s explicitnim  $W_r^{(l)} \cdot h_s^{(l)}$.}
Each message is then divided by a normalization constant
$c_{s,d} = \sqrt{\card{\mathcal{N}_s^r}} \sqrt{\card{\mathcal{N}_d^r}}$ \cite{kipf2017semisupervised},
where $\mathcal{N}_n^r$ is the set of neighbors of node $n$ under the relation $r$.
\todo{FB: Mention that we mean both in- and out-neighbors?}
Once all the messages are computed,
they are aggregated by the destination nodes to form the new node embedding.
Each node $d$ aggregates all the incoming messages of a given edge type $r$ by summation,
then passes the sum through an activation function $\sigma$ such as the \gls{relu},
and finally aggregates the messages across the edge types by summation,
yielding the new embedding $h_d^{(l+1)}$.
The following formula captures the update of embedding of node $d$:
$$
h_d^{(l+1)} =
\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (h_s^{(l)} W_r^{(l)} + b_r^{(l)})}
$$
%$$
%h_i^{(l+1)} =
%\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
%$$
% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
%\todo{FB: Mention inspiration: Transformer. See Straka's slides.}

@@

The symbol cost of each symbol is computed by passing the symbol's embedding through a dense layer with a single output unit.
No activation function is applied so that the output values can span the whole $\re$.
\todo{MS: provided the input embeddings can...}

Note that it is possible to use a more complex projection module,
e.g., a feed-forward network with one or more hidden layers.
\todo{FB: Ensure the term is defined.}
Our experiments showed no significant improvement when a hidden layer was added,
likely because the underlying \gls{gcn} learns a sufficiently complex transformation.

@@

\begin{proof}
We prove the lemma by contradiction.
Let $\pi$ minimize $C$ and let $\pi$ not rank the costs in non-increasing order.
Then there exist $k < l$ such that $c(\pi(k)) < c(\pi(l))$.
Let $\bar{\pi}$ be a precedence obtained from $\pi$ by swapping the elements $k$ and $l$.
Then we obtain
%$\bar{\pi} = (\pi(1), \ldots, \pi(k-1), \pi(l), \pi(k+1), \ldots, \pi(l-1), \pi(k), \pi(l+1), \ldots, \pi(n))$.
\begin{align*}
C(\bar{\pi}) - C(\pi)
&= kc(\bar{\pi}(k)) + lc(\bar{\pi}(l)) - kc(\pi(k)) - lc(\pi(l)) \\
&= kc(\pi(l)) + lc(\pi(k)) - kc(\pi(k)) - lc(\pi(l)) \\
&= k(c(\pi(l)) - c(\pi(k))) - l(c(\pi(l)) - c(\pi(k))) \\
&= (k-l) (c(\pi(l)) - c(\pi(k))) \\
&< 0
\end{align*}
The final inequality is because $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
Thus, $C(\bar{\pi}) < C(\pi)$, which is contradicts the assumption that $\pi$ minimizes $C$. \qed
\end{proof}

Once the symbol costs are known,
producing a precedence that minimizes the precedence cost is cheap
because ranking is a fast operation.\todo{MS: can we not say ``sorting''? Also slightly earlier.}

Note that a precedence that minimizes $C$\todo{MS: Indefinite article; there can be more than one such...}
orders the symbols with the lowest cost as the last, prioritizing them for early inferences.

\todo[inline]{FB: Why is the equality predicate always the first in the precedence?
MS: Andrei Voronokov reasons. It's typically better in practice to postpone equational reasoning,
so we want equalities to be generally small.}
\todo[inline]{FB: Mention that the common heuristics fit this scheme.}

@@

In \cref{sec:graphifier,sec:gcn,sec:output,sec:ranking} we described the structure of a recommender system that generates a precedence for an arbitrary input problem.
The efficacy of the recommender depends on the quality of the underlying symbol cost function.
In theory, the symbol cost function can assign the costs so that
ranking the symbols by their costs yields an optimum precedence,
\todo{MS: hezky, to zacina dobre!}
and all the information necessary to determine the optimum precedence is present in the graph representation of the input problem.
\todo{MS: ``because the of the lossless property of the graph encoding mentioned before.''
(Na druhou stranu nevime, jestli to dokaze zvladnout navrzena architectura.)}
\todo{MS: Hlavne tady ale jakoby chybi druha pulky ty vety. Neco jako ``In practice, however, ...'' Nemyslis?} 
Our approach to defining an appropriate symbol cost function is based on statistical learning
from executions of an \gls{atp} on a set of problems with various\todo{MS: proc ne ``random''?} precedences.

@@

Each training example has the form $(P, \PrecBetter, \PrecWorse)$,
where $P = (\Sigma, \mathit{Cl})$ is a problem
and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
such that the prover using $\PrecBetter$ solves $P$ in fewer iterations of the saturation loop than with $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}$.\todo{MS: Could we have $\PrecBetter \prec_P\PrecWorse$?}
\todo{Is this sufficient?}

@@

\todo{Two levels of proxy metrics: 0-1 loss, differentiable loss (hinge, logistic)}
To ensure that ranking the symbols by their costs
yields a good precedence,
we want the symbol cost function $c$
to satisfy the inequality $C(\PrecBetter) < C(\PrecWorse)$
for as many training examples $(P, \PrecBetter, \PrecWorse)$ as possible.
%
This can alternatively be expressed as $s(\PrecBetter, \PrecWorse) := C(\PrecBetter) - C(\PrecWorse) < 0$,
introducing a new quantity
$s(\PrecBetter, \PrecWorse)$
as the \emph{score} of the (ordered) precedence pair $(\PrecBetter, \PrecWorse)$.
Given a set of examples of the form $(P, \PrecBetter, \PrecWorse)$
where $\Better{\PrecBetter}{\PrecWorse}$,
our goal is to maximize the accuracy
$\frac{1}{m} \sum_x \iverson{s(\PrecBetter, \PrecWorse) < 0}$.
\todo{MS: Not sure if we can assume $\iverson{X}$ to be universally understandable.}
% Alternative: We actually don't care about the relative order of non-minimum precedences.

A common approach to training a binary classifier\todo{MS: First mention of a ``binary classifier''!
We classify the examples, sure, but you did not say it yet.}
is to relax the non-differentiable accuracy $\iverson{s(\PrecBetter, \PrecWorse) < 0}$
to a differentiable proxy
such as the logistic loss
$L = - \log \sigmoid s(\PrecBetter, \PrecWorse)$.
\todo{MS: neni tu ted spatne zniminko? Nebo spis uz v definici score? Cekal bych, ze pro positivni examply (coz jsou u nas vsechny)
bude chit $s$ kladne.}
